Joint analysis of read count data

### 2020-09-04 combined_analysis/combine_all_data.Rmd
Fix Dx

L = cbind(	Scz = L_SCZ, 
			BP 	= L_BP, 
			Sex = L_sex)
plotContrasts(L) + theme()

fit_marginal = dream(vobj[1:10,], form, METADATA, L=L,BPPARAM = SnowParam(18))
```

>>>>

L = cbind(	Scz = L_SCZ, 
			BP 	= L_BP, 
			Sex = L_sex)

plotContrasts(L) + theme(axis.text.x=element_text(angle = 45, vjust = 1, hjust=1))

fit_marginal = dream(vobj, form, METADATA, L=L,BPPARAM = SnowParam(18))
```
